### 2021-07-13 src/paper/literature_review.tex
work on literature review.

The workhorse model in epidemiology is the SEIR model. However, The traditional SEIR
model is not fine-grained enough to model nuanced policies.\comment[id=HM]{Still old
motivation. Hard to get the timing of tests and results right?} This has motivated a
large number of researchers to extend the standard model to allow for more heterogeneity
and flexibility. Examples are \citet{Grimm2020}, \citet{Donsimoni2020} and
\citet{Acemoglu2020}\comment[id=HM]{We need to cite more strategically. Cut Grimm,
Donsinomi. More state of the art SEIR in other fields. Or drop SEIR altogether? If I
read that as a Michael Meyer-Hermann type, I would think, ``ah, these economists
again...''} who develop multi group SEIR models to analyze the effects of targeted
lockdowns and \citet{Berger2020} who extend the SEIR model to analyze testing and
conditional quarantines. For a more comprehensive review see \citet{Avery2020}. Others
have used the results of a standard SEIR model as input for economic models that
estimate the cost of policies (e.g. \citet{Dorn2020}).

While the popularity of the SEIR model is mainly due to its simplicity, the extensions
are quite complex. It is unlikely that there will be a SEIR model that combines all
proposed extensions. Moreover, the extensions do not address other key issues: The main
parameter of the SEIR model, the basic reproduction number ($R_0$), is not
policy-invariant. It is a composite of the number of contacts each person has and the
infection probability of the contacts. In fact, policy simulations are done by setting
$R_0$ to a different value but it is hard to translate a real policy into the value of
$R_0$ it will induce. In other words, SEIR models are not suited for evaluating the
effect of policies which have never been experienced before.

Another commonly used model class in epidemiology are agent-based simulation
models. In a prototypical agent-based simulation model, individuals are
simulated as moving particles. Infections take place when two particles come closer than
a certain contact radius (e.g. \citet{Silva2020} and \citet{Cuevas2020}). While the
simulation approach makes it easy to incorporate heterogeneity in disease progression, it
is hard to incorporate heterogeneity in meeting patterns. Moreover, policies are modeled
as changes in the contact radius or momentum equation of the particles. The translation
from real policies to corresponding model parameters is a hard task.

@@

\citet{Aleta2020} develop an agent-based simulation model with a very high geographical
resolution by estimating contact networks from fine grained mobility data for the
Boston metropolitan area. They use this model to show how NPIs, contact tracing and PCR
testing can influence the infection dynamics. However, they do not calibrate their model
match actual infection numbers which makes it more suitable to explore the general
mechanics of different disease mitigation measures than for their quantitative
evaluation.

\citet{Bicher2021} simulate the Austrian population during the first wave (February 21
to April 9, 2020). It uses the same data provided by \citet{Mossong2008} as we use to
calibrate contact networks for households, workplaces and schools. The model focuses on
analyzing the effect of different contact tracing strategies.

Moreover, there are several forthcoming applications\comment[id=HM]{What is that
supposed to mean?} of agent-based simulation models with contact networks. Examples are
\citet{Basurto2020}, \citet{DelliGatti2020} and \citet{Mellacher2020}.

Our model combines elements from the above models and adds several new features. To
the best of our knowledge, ours is the only model that can explain observed case
numbers with an excellent fit over more than 9 Months. We also have the most fine
grained model of schools and NPIs that affect schools. Finally, we have an extremely
detailed model of PCR and rapid tests with a share of detected cases that varies over
time and across age groups.

>>>>

A commonly used model class in epidemiology are agent-based simulation
models. In a prototypical agent-based simulation model, individuals are
simulated as moving particles. Infections take place when two particles come closer than
a certain contact radius (e.g. \citet{Silva2020} and \citet{Cuevas2020}). While the
simulation approach makes it easy to incorporate heterogeneity in disease progression, it
is hard to incorporate heterogeneity in meeting patterns. Moreover, policies are modeled
as changes in the contact radius or momentum equation of the particles. The translation
from real policies to corresponding model parameters is a hard task.

@@

\citet{Aleta2020} develop an agent-based simulation model with a very high geographical
resolution by estimating contact networks from fine grained mobility data for the
Boston metropolitan area. They use this model to show how NPIs, contact tracing and PCR
testing can influence the infection dynamics. However, they do not calibrate their model
to match actual infection numbers which makes it more suitable to explore the general
mechanics of different disease mitigation measures than for their quantitative
evaluation.

\citet{Bicher2021} simulate the entire Austrian population. The use data from the first
wave (February 21 to April 9, 2020) to calibrate ther model and predict the effect of
different NPIs and contact tracing policies until November 2020. They the same data
provided by \citet{Mossong2008} as we use to calibrate contact networks for households,
workplaces and schools. The model focuses on analyzing the effect of different contact
tracing strategies and not on modelling enacted Austrian policies over a long period
of time.

Moreover, there are several forthcoming applications\comment[id=HM]{What is that
supposed to mean?}\comment[id=J]{Does that mean we should not cite the working
papers here?} of agent-based simulation models with contact networks. Examples are
\citet{Basurto2020}, \citet{DelliGatti2020} and \citet{Mellacher2020}.

Our model combines elements from the above models and adds other ones. To the best of
our knowledge, our model is the only one with the following features:

1. The free model parameters have been estimated with the method of simulated moments
\citep{McFadden1989}. Despite having few free parameters our model does en excellent
job in explaining observed case numbers and the spread of the B.1.1.7 mutation over
more than nine months of data.

2. We have an extremely fine grained of schools and preschools.
We can thus easily model all NPIs that have been implemented in Germany in the past 9
months. This includes complete school closures, phases where only those students whose
parents could not find any private childcare arrangement could attend, split class
approaches for some or all age groups and combinations thereof. Moreover, we can
account for additional hygiene measures whose effect is estimated inside the model.

3. we model the evolution of the pandemic and all enacted policies over since the
start of the second wave. Since the vast majority of cases has occurred in that time
period and we also model unobserved infections our simulations take into account that
many people are already immune because they are recovered from an infection and that
this immunity is not spread randomly across the population.

4. We have an extremely detailed model of PCR and rapid tests with a share of detected
cases that varies over time and across age groups. We fit estimates of the share of
known cases from other studies for time periods where those are available but also
estimate a plausible share of known cases after vaccinations become widespread and
methodologies that rely on a case fatality ratio to identify the share of known
cases are not applicable anymore.
